Introduction to Markov state modeling with the PyEMMA software --- v\versionnumber

### 2018-11-16 manuscript/manuscript.tex
[manuscript] make caption fig 4 self-containing #171 [ci skip]

\begin{figure}
\includegraphics{figure_4}
\caption{Example analysis of the conformational dynamics of a pentapeptide backbone:
(a)~The convergence behavior of the implied timescales associated with the four slowest processes.
(b)~Chapman-Kolmogorov test computed using an MSM estimated with lag time $\tau=0.5$~ns assuming~5 metastable states.
The solid lines in (a) refer to the maximum likelihood result while the dashed lines show the ensemble mean computed with a Bayesian sampling procedure~\cite{ben-rev-msm}.
The black line indicates where implied timescales are equal to the lag time,
whereas the grey area indicates all implied timescales faster than the lag time.
In both panels, the (non-grey) shaded areas indicate~$95\%$ confidence intervals computed with the aforementioned Bayesian sampling procedure.}
\label{fig:its-and-ck}
\end{figure}

>>>>

\begin{figure}
\includegraphics{figure_4}
\caption{Example analysis of the conformational dynamics of a pentapeptide backbone:
(a)~The convergence behavior of the implied timescales associated with the four slowest processes.
The solid lines refer to the maximum likelihood result while the dashed lines show the ensemble mean computed with a Bayesian sampling procedure~\cite{ben-rev-msm}.
The black line (marking equality of timescale and lag time) with grey area indicates the timescale horizon beyond which the MSM cannot resolve processes.
As implied timescales are well-converged at $\tau=0.5$~ns, this lag time is chosen for subsequent MSM estimation.
(b)~Chapman-Kolmogorov test computed using an MSM estimated with lag time $\tau=0.5$~ns assuming~5 metastable states.
Predictions from this model agree with higher lag time estimates within confidence intervals.
Implied timescales convergence as well as a passing Chapman-Kolmogorov test are a necessary condition in MSM validation.
In both panels, the (non-grey) shaded areas indicate~$95\%$ confidence intervals computed with the aforementioned Bayesian sampling procedure.}
\label{fig:its-and-ck}
\end{figure}
